XOR power analysis

### 2021-09-17 analysis/power/xor-some_power.Rmd
refactor, add init simulation for Bayesian power analysis

First, the preprocessed and tidy wide pilot data is read and combined. It comprises data from N = 140 subjects after exclusions in total.
```{r, echo=FALSE}
pilot1 <- read_csv("./../data/pilots/pilot2_critical_zScore_wide_tidy.csv") %>%
  select(-competence_wUtt, -relevance_wUtt)
pilot2 <- read_csv("./../data/pilots/pilot3_critical_zScore_wide_tidy.csv")

>>>>

First, the preprocessed and tidy wide pilot data is read and combined. It comprises data from N = 140 subjects after exclusions in total.
```{r, echo=FALSE}
pilot1 <- read_csv("./../../data/pilots/pilot2_critical_zScore_wide_tidy.csv") %>%
  select(-competence_wUtt, -relevance_wUtt)
pilot2 <- read_csv("./../../data/pilots/pilot3_critical_zScore_wide_tidy.csv")
